---

title: "Prevalance Markdown"
author: "Michael Lee"
date: "10/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Intro
The purpose of this code file is to provide the prevalence estimates of sea lice
from the data, as well as the averages and sums and output a plot. The majority
of the code is designed to clean the code and formatting to ensure it works 
optimally for R.  
## Working Directory
The working directory sets up the paths for the file the code works out of. It
also creates the folders where we can access and create plots and the data files

```{r Working Directory}
wd <- "~/Sea-Lice-Analysis-2021"  
getwd()
setwd(wd)
folders <- c("Code", "Data", "OutputFigures", "OutputData")

# function to create folders below
for(i in 1:length(folders)){
  if(file.exists(folders[i]) == FALSE)
    dir.create(folders[i])
}

# we also need to store the paths to these new folders

code.output.path <- paste(wd, "/", folders[1], sep = "")
data.input.path <- paste(wd, "/", folders[2], sep = "")
figures.path <- paste(wd, "/", folders[3], sep = "")
data.output.path <- paste(wd, "/", folders[4], sep = "")

# our raw data is stored in different folders, lets make the paths
sealicedata.path <- paste(getwd(), "/Data", "/", sep = "")

# now we can access and save stuff to these folders!
```

## Cleaning the Code
The code needs to clean up the data within the csv file. We also need to install
several packages to make the code work with the commands given. The cleaning of 
the code refers to the year, salmon species, location, and categories of sea 
lice.The purpose of this section is to make sure that all the unique categories 
are consistent. For example, there are locations where the names have an 
additional space in it, which R doesn't recognize as the same location. Performs
the same job as the code cleaning in the Abundance Code file. 
```{r Cleaning the Code}
#x# time to upload the datas into folder
sealicedata <- read.csv(paste(sealicedata.path, "/", "CCFS_SeaLice_Monitoring_2021.csv",
                              sep = ""), stringsAsFactors = FALSE)


#unhashtag to install packages below 
#install.packages(c("boot", "MASS","plyr","dplyr", "ggplot2", "tibble", "car", "reshape2",
#                  "epitools", "readxl", "tidyverse","arsenal")))
library(boot)
library(MASS)
library(plyr)
library(dplyr)
library(ggplot2)
library(tibble)
library(car)
library(reshape2)
library(epitools)
library(readxl)
library(tidyverse)
library(readr)
library(arsenal)

#pacman::p_load(tidyverse,nlme,emmans,here)
#pacman::p_load(ggthemes, ggplot2)

source("https://raw.githubusercontent.com/koundy/ggplot_theme_Publication/master/ggplot_theme_Publication-2.R")


warnings()

#***************************CLEANING
#x#cleaning time
#adjusting datas***********************
sealicedata$year<-as.numeric(sealicedata$year)
#adjusting dates to date format
sealicedata$date <- as.Date(with(sealicedata, 
                                 paste(year, month, day, sep="-")), "%Y-%m-%d")
#height -> as.numeric
sealicedata$height<-as.numeric(sealicedata$height)
#making it all a df
sealicedata<-data.frame(sealicedata)
#changing na's to 0's
sealicedata[ , 12:26][is.na(sealicedata[ , 12:26] ) ] <- 0 
#col 1 to "fish_id"
names(sealicedata)[1]<-paste("fish_id")
#na's to 0 in sum_all_lice
sealicedata$sum_all_lice[is.na(sealicedata$sum_all_lice)]<-0

sealicedata <- sealicedata %>% rowwise() %>%
  dplyr::mutate(sum_all_lice = sum(c_across(Lep_cope:unid_adult)))

salmcounts <- sealicedata %>%
  select( Lep_cope, chalA, chalB, Lep_PAmale, Lep_PAfemale, Lep_male,
          Lep_nongravid, Lep_gravid, Caligus_cope, Caligus_mot, Caligus_gravid, unid_cope,
          chal_unid,unid_PA, unid_adult)

# RM defining categories of lice.

#motile lice sub
motlice<-sealicedata[,c("Caligus_mot", "Caligus_gravid", "Lep_gravid", "Lep_nongravid", "Lep_male", "Lep_PAfemale", "Lep_PAmale", "unid_PA", "unid_adult")]
#cope lice sub
copes<-sealicedata[,c("Lep_cope", "Caligus_cope", "unid_cope")]
#chalimus lice sub
chals<-sealicedata[,c("chalA", "chalB", "chal_unid")]
#attached lice sub
attlice<-sealicedata[,c("Lep_cope","chalA","chalB","Caligus_cope","unid_cope","chal_unid")]


#X# List character variables and go through one by one
list(unique(colnames(sealicedata)))
#make sure year is consistent and case sensitive
list(unique(sealicedata$year))
#make sure names of species are correct
list(unique(sealicedata$species))
#fixing species names
sealicedata$species[sealicedata$species == "chum "]<- "chum"
sealicedata$species[sealicedata$species == "coho "]<- "coho"
sealicedata$species[sealicedata$species == "chinook "]<- "chinook"




#adjusting sample locations
#list locations
list(unique(sealicedata$location))

#adjusting names based on list output
#x#fix errors in names, do this by inputing the incorrect/ current name into the brackets, 
#and then the corrected version into the assigned end <-

#Bedwell Sound North Fix
sealicedata$location[sealicedata$location == "Bedwell Estuary "]<- "Bedwell Sound North"
sealicedata$location[sealicedata$location == "Bedwell estuary"]<- "Bedwell Sound North"
#Currently Bedwell Estuary is mapped as multiple locations, several close to the estuary and
#several near Bedwell Sound Middle: NEED TO FIX
#sealicedata$location[sealicedata$location == "Bedwell Estuary"]<- "Bedwell Sound North"
sealicedata$location[sealicedata$location ==  "Bedwell River"]<-"Bedwell Sound North"
sealicedata$location[sealicedata$location == "Bedwell Estuary 4"]<- "Bedwell Sound North"
sealicedata$location[sealicedata$location == "Bedwell estuary 4"]<- "Bedwell Sound North"

#Bedwell Sound Middle Fix
sealicedata$location[sealicedata$location == "Bedwell 2 "]<- "Bedwell Sound Middle"
sealicedata$location[sealicedata$location == "Bedwell estuary 3"]<- "Bedwell Sound Middle"
sealicedata$location[sealicedata$location == "Bedwell Estuary 3"]<- "Bedwell Sound Middle"
sealicedata$location[sealicedata$location == "Bedwell estuary 2"]<- "Bedwell Sound Middle"
sealicedata$location[sealicedata$location == "Bedwell Estuary 2"]<- "Bedwell Sound Middle"
sealicedata$location[sealicedata$location ==  "Bedwell 2"]<-"Bedwell Sound Middle"
sealicedata$location[sealicedata$location ==  "Sniffles"]<-"Bedwell Sound Middle"
sealicedata$location[sealicedata$location ==  "Sniffles 2"]<-"Bedwell Sound Middle"


#Bedwell Sound South Fix
sealicedata$location[sealicedata$location ==  "Bedwell 3"]<- "Bedwell Sound South"

#Cypre Fix
sealicedata$location[sealicedata$location == "Cypre "]<- "Cypre River"

#North Meares Fix
sealicedata$location[sealicedata$location == "Meares North"]<- "North Meares"

#White Pine Fix
sealicedata$location[sealicedata$location == "White Pine "]<- "White Pine"

#Ritchie Bay Fix
sealicedata$location[sealicedata$location == "Ritchie Bay "]<- "Ritchie Bay"

#Tranquil Fix
sealicedata$location[sealicedata$location == "Tranquil estuary"]<- "Tranquil Estuary"

list(unique(sealicedata$location))


#X#change year to current



#subset to adjust for year

sealice.current<-sealicedata

length(unique(sealice.current$location))

#adjust for our focus species
sealice.current <- sealice.current<-data.frame(subset(sealice.current,
                                                      species == "chum"))

salmcounts <- sealice.current %>%
  select( Lep_cope, chalA, chalB, Lep_PAmale, Lep_PAfemale, Lep_male,
          Lep_nongravid, Lep_gravid, Caligus_cope, Caligus_mot, Caligus_gravid, unid_cope,
          chal_unid,unid_PA, unid_adult)

# RM defining categories of lice.

#motile lice sub
motlice<-sealice.current[,c("Caligus_mot", "Caligus_gravid", "Lep_gravid", "Lep_nongravid", "Lep_male", "Lep_PAfemale", "Lep_PAmale", "unid_PA", "unid_adult")]
#cope lice sub
copes<-sealice.current[,c("Lep_cope", "Caligus_cope", "unid_cope")]
#chalimus lice sub
chals<-sealice.current[,c("chalA", "chalB", "chal_unid")]
#attached lice sub
attlice<-sealice.current[,c("Lep_cope","chalA","chalB","Caligus_cope","unid_cope","chal_unid")]

#total lice sub
sealice.current <- sealice.current %>% rowwise() %>%
  dplyr::mutate(Sum_all_lice = sum(c_across(colnames(salmcounts)))) 

#Below gives columns of summed motiles, attached, copepodids, chalimus, and total counts. Useful for prevalence and abundance plots.
sealice.current$motsum<-rowSums(motlice, na.rm = TRUE)
sealice.current$copsum<-rowSums(copes, na.rm = TRUE)
sealice.current$chalsum<-rowSums(chals, na.rm = TRUE)
sealice.current$attachedsum<-rowSums(attlice, na.rm = TRUE)
sealice.current$sum_all_lice<-rowSums(salmcounts, na.rm = T)

# ensuring the column class is numeric
sealice.current$motsum<- as.numeric(sealice.current$motsum)
sealice.current$copsum<- as.numeric(sealice.current$copsum)
sealice.current$chalsum<-as.numeric(sealice.current$chalsum)
sealice.current$attachedsum<-as.numeric(sealice.current$attachedsum)
sealice.current$sum_all_lice<-as.numeric(sealice.current$sum_all_lice)
```
## Abundance Estimates
Bootstrapping is necessary to sample non parametric data. Similar to the 
abundance file, we need to find the weekly intervals for the data. This is 
setting up the functions for each species. 
```{r Abundance Estimates}
#Setting the cap for bootstrapping
n.boot.b<-1000

##ASSIGNING WEEKLY INTERVALS TO ALL THE dates in the abundance.base data set 
#weekly intervals.
#set up vectors to hold data

#X#beginning abundance plots, start bye creating a list function. 
#x#Start of Abundance Plot #1 for first Location in list
#Then determine how long the list is and replicate the following code that many times, only changing the x in base.list[x,] below
#you should replicate this whole code for every location sampled, unless there are not enough samples, rmeber each site needs a min of 30
base.list <- data.frame(unique(sealice.current$location))
list(base.list)
#starting with the first river in the list, 1

abundance.base<- sealice.current
```
## Chum Function
The purpose of the function is to remove dates where >30 fish were caught. 
Turning dates into Julian to make it easier to process with R. Establishing 
weekly intervals to group dates and samples to take average from.
```{r Chum Function}
## Taking out the dates where less than 30 fish were caught
## Creating a weekly interval column
####################################################################################################
a.b.prod <- data.frame(abundance.base[1,])
a.b.prod <- a.b.prod[-1,]


for(j in 1:nrow(base.list)){

  abundance.base<-data.frame(subset(sealice.current, location == base.list[j,]))

  # Removing any dates with less than 30 fish
  
  
  ## Making julian dates
  abundance.base$date <- as.Date(with(abundance.base, paste(year, month, day, sep="-")), "%Y-%m-%d")
  abundance.base$date  <- julian(abundance.base$date) 
  datelist <-(abundance.base$date)
  ## Making a new column for weeklyinterval dates
  abundance.base$weeklyintvl<-rep(0, each = length(abundance.base$date))
  
  ## Finding the weekly intervals
  value <- abundance.base$weeklyintvl
  # all dates next to an empty column
  dat <- data.frame(datelist, value)
  # vector of all the unique dates
  dates = unique(dat$date)
  # vector for the number of rows for each date
  count <- c()
  
  for(i in 1:length(dates)){
    # length of the subset associated with each date
    n <- length(which(dat$datelist == dates[i]))
    # put the count into the empty vector
    count[i] <- n
  }
  # each unique date has a count of it's rows (assuming each row is a fish)
  output1 <- data.frame(dates, count)
  
  # Here you just turn dates into julian dates for ease later on
  #cbind to as.date version
  abundance.base$date <- as.Date(with(abundance.base, paste(year, month, day, sep="-")), "%Y-%m-%d")
  datelist <-(abundance.base$date)
  abundance.base$weeklyintvl<-rep(0, each = length(abundance.base$date))
  value <- abundance.base$weeklyintvl
  dat <- data.frame(datelist, value)
  dates = unique(dat$date)
  count <- c()
  for(i in 1:length(dates)){
    n <- length(which(dat$datelist == dates[i]))
    count[i] <- n
  }
  output2 <- data.frame(dates, count)
  
  #cbind outputs
  output.date <- cbind(output1,output2)
  output.date = subset(output.date, select = -c(count))
  
  #subset to remove dates with less than 30 fish
  remove.dates <- subset(output.date$dates.1, count < 30)
  #remove.dates <- as.Date(subset(output.date$dates, count <30)
  remove.dates <- data.frame(remove.dates)
  #remove dates from main data
  abundance.base$date  <- as.Date(abundance.base$date) 
  require(lubridate)
  class(remove.dates[,])
  class(abundance.base$date)
  list(remove.dates)
  
  #x# from the list above, input the dates into the filter function below by their column number
  if(nrow(remove.dates)>0){
    for(i in 1:nrow(remove.dates)){
      abundance.base <- abundance.base %>%
        filter(date != remove.dates[i,])#%>%
      #filter(date != as.Date(remove.dates[2,])) 
      #  filter(date != as.Date(remove.dates[,])) # unsure if this second line will cause problems
    }
  }
  
  #try <- abundance.base[(abundance.base$date != remove.dates[,]),]
  remove.dates
  unique(abundance.base$date)
  a.b.prod <- rbind(a.b.prod,abundance.base)
}
abundance.base <- a.b.prod # this is redundant but was kept to work with the rest of the code which calls on abundance.base


chum <- abundance.base

```
## Chinook Cleaning and Function
Same as the chum function and cleanup section, 
but applied for the Chinook species. 
```{r Chinook Cleaning}
sealice.current<-sealicedata

length(unique(sealice.current$location))

#adjust for our focus species
sealice.current <- sealice.current<-data.frame(subset(sealice.current, species == "chinook"))

salmcounts <- sealice.current %>%
  select( Lep_cope, chalA, chalB, Lep_PAmale, Lep_PAfemale, Lep_male,
          Lep_nongravid, Lep_gravid, Caligus_cope, Caligus_mot, Caligus_gravid, unid_cope,
          chal_unid,unid_PA, unid_adult)

# RM defining categories of lice.

#motile lice sub
motlice<-sealice.current[,c("Caligus_mot", "Caligus_gravid", "Lep_gravid", "Lep_nongravid", "Lep_male", "Lep_PAfemale", "Lep_PAmale", "unid_PA", "unid_adult")]
#cope lice sub
copes<-sealice.current[,c("Lep_cope", "Caligus_cope", "unid_cope")]
#chalimus lice sub
chals<-sealice.current[,c("chalA", "chalB", "chal_unid")]
#attached lice sub
attlice<-sealice.current[,c("Lep_cope","chalA","chalB","Caligus_cope","unid_cope","chal_unid")]

#total lice sub
sealice.current <- sealice.current %>% rowwise() %>%
  dplyr::mutate(Sum_all_lice = sum(c_across(colnames(salmcounts)))) 

#Below gives columns of summed motiles, attached, copepodids, chalimus, and total counts. Useful for prevalence and abundance plots.
sealice.current$motsum<-rowSums(motlice, na.rm = TRUE)
sealice.current$copsum<-rowSums(copes, na.rm = TRUE)
sealice.current$chalsum<-rowSums(chals, na.rm = TRUE)
sealice.current$attachedsum<-rowSums(attlice, na.rm = TRUE)
sealice.current$sum_all_lice<-rowSums(salmcounts, na.rm = T)

# ensuring the column class is numeric
sealice.current$motsum<- as.numeric(sealice.current$motsum)
sealice.current$copsum<- as.numeric(sealice.current$copsum)
sealice.current$chalsum<-as.numeric(sealice.current$chalsum)
sealice.current$attachedsum<-as.numeric(sealice.current$attachedsum)
sealice.current$sum_all_lice<-as.numeric(sealice.current$sum_all_lice)

```
```{r Chinook Function}
#Setting the cap for bootstrapping
n.boot.b<-1000

##ASSIGNING WEEKLY INTERVALS TO ALL THE dates in the abundance.base data set 
#weekly intervals.
#set up vectors to hold data

#X#beginning abundance plots, start bye creating a list function. 
#x#Start of Abundance Plot #1 for first Location in list
#Then determine how long the list is and replicate the following code that many times, only changing the x in base.list[x,] below
#you should replicate this whole code for every location sampled, unless there are not enough samples, rmeber each site needs a min of 30
base.list <- data.frame(unique(sealice.current$location))
list(base.list)

  # 1
  ####################################################################################################
  ## Taking out the dates where less than 30 fish were caught
  ## Creating a weekly interval column
  ####################################################################################################
  a.b.prod <- data.frame(abundance.base[1,])
  a.b.prod <- a.b.prod[-1,]
  
  
  for(j in 1:nrow(base.list)){

    abundance.base<-data.frame(subset(sealice.current, location == base.list[j,]))

    # Removing any dates with less than 30 fish
    
    
    ## Making julian dates
    abundance.base$date <- as.Date(with(abundance.base, paste(year, month, day, sep="-")), "%Y-%m-%d")
    abundance.base$date  <- julian(abundance.base$date) 
    datelist <-(abundance.base$date)
    ## Making a new column for weeklyinterval dates
    abundance.base$weeklyintvl<-rep(0, each = length(abundance.base$date))
    
    ## Finding the weekly intervals
    value <- abundance.base$weeklyintvl
    # all dates next to an empty column
    dat <- data.frame(datelist, value)
    # vector of all the unique dates
    dates = unique(dat$date)
    # vector for the number of rows for each date
    count <- c()
    
    for(i in 1:length(dates)){
      # length of the subset associated with each date
      n <- length(which(dat$datelist == dates[i]))
      # put the count into the empty vector
      count[i] <- n
    }
    # each unique date has a count of it's rows (assuming each row is a fish)
    output1 <- data.frame(dates, count)
    
    # Here you just turn dates into julian dates for ease later on
    #cbind to as.date version
    abundance.base$date <- as.Date(with(abundance.base, paste(year, month, day, sep="-")), "%Y-%m-%d")
    datelist <-(abundance.base$date)
    abundance.base$weeklyintvl<-rep(0, each = length(abundance.base$date))
    value <- abundance.base$weeklyintvl
    dat <- data.frame(datelist, value)
    dates = unique(dat$date)
    count <- c()
    for(i in 1:length(dates)){
      n <- length(which(dat$datelist == dates[i]))
      count[i] <- n
    }
    output2 <- data.frame(dates, count)
    
    #cbind outputs
    output.date <- cbind(output1,output2)
    output.date = subset(output.date, select = -c(count))
    
    #subset to remove dates with less than 30 fish
    remove.dates <- subset(output.date$dates.1, count < 30)
    #remove.dates <- as.Date(subset(output.date$dates, count <30)
    remove.dates <- data.frame(remove.dates)
    #remove dates from main data
    abundance.base$date  <- as.Date(abundance.base$date) 
    require(lubridate)
    class(remove.dates[,])
    class(abundance.base$date)
    list(remove.dates)
    
    #x# from the list above, input the dates into the filter function below by their column number
    if(nrow(remove.dates)>0){
      for(i in 1:nrow(remove.dates)){
        abundance.base <- abundance.base %>%
          filter(date != remove.dates[i,])#%>%
        #filter(date != as.Date(remove.dates[2,])) 
        #  filter(date != as.Date(remove.dates[,])) # unsure if this second line will cause problems
      }
    }
    
    #try <- abundance.base[(abundance.base$date != remove.dates[,]),]
    remove.dates
    unique(abundance.base$date)
    a.b.prod <- rbind(a.b.prod,abundance.base)
  }
  abundance.base <- a.b.prod # this is redundant but was kept to work with the rest of the code which calls on abundance.base

chinook <- abundance.base
```
## Coho Cleaning and Function
Same as the previous salmon species sections (Chum and Chinook), but applied for
Coho.
```{r Coho Cleaning}
sealice.current<-sealicedata

length(unique(sealice.current$location))

#adjust for our focus species
sealice.current <- sealice.current<-data.frame(subset(sealice.current, species == "coho"))

salmcounts <- sealice.current %>%
  select( Lep_cope, chalA, chalB, Lep_PAmale, Lep_PAfemale, Lep_male,
          Lep_nongravid, Lep_gravid, Caligus_cope, Caligus_mot, Caligus_gravid, unid_cope,
          chal_unid,unid_PA, unid_adult)

# RM defining categories of lice.

#motile lice sub
motlice<-sealice.current[,c("Caligus_mot", "Caligus_gravid", "Lep_gravid", "Lep_nongravid", "Lep_male", "Lep_PAfemale", "Lep_PAmale", "unid_PA", "unid_adult")]
#cope lice sub
copes<-sealice.current[,c("Lep_cope", "Caligus_cope", "unid_cope")]
#chalimus lice sub
chals<-sealice.current[,c("chalA", "chalB", "chal_unid")]
#attached lice sub
attlice<-sealice.current[,c("Lep_cope","chalA","chalB","Caligus_cope","unid_cope","chal_unid")]

#total lice sub
sealice.current <- sealice.current %>% rowwise() %>%
  dplyr::mutate(Sum_all_lice = sum(c_across(colnames(salmcounts)))) 

#Below gives columns of summed motiles, attached, copepodids, chalimus, and total counts. Useful for prevalence and abundance plots.
sealice.current$motsum<-rowSums(motlice, na.rm = TRUE)
sealice.current$copsum<-rowSums(copes, na.rm = TRUE)
sealice.current$chalsum<-rowSums(chals, na.rm = TRUE)
sealice.current$attachedsum<-rowSums(attlice, na.rm = TRUE)
sealice.current$sum_all_lice<-rowSums(salmcounts, na.rm = T)

# ensuring the column class is numeric
sealice.current$motsum<- as.numeric(sealice.current$motsum)
sealice.current$copsum<- as.numeric(sealice.current$copsum)
sealice.current$chalsum<-as.numeric(sealice.current$chalsum)
sealice.current$attachedsum<-as.numeric(sealice.current$attachedsum)
sealice.current$sum_all_lice<-as.numeric(sealice.current$sum_all_lice)


```
```{r Coho Function}
#Setting the cap for bootstrapping
n.boot.b<-1000

##ASSIGNING WEEKLY INTERVALS TO ALL THE dates in the abundance.base data set 
#weekly intervals.
#set up vectors to hold data

#X#beginning abundance plots, start bye creating a list function. 
#x#Start of Abundance Plot #1 for first Location in list
#Then determine how long the list is and replicate the following code that many times, only changing the x in base.list[x,] below
#you should replicate this whole code for every location sampled, unless there are not enough samples, rmeber each site needs a min of 30
base.list <- data.frame(unique(sealice.current$location))
list(base.list)
abundance.base <- sealice.current

  # 1
  ####################################################################################################
  ## Taking out the dates where less than 30 fish were caught
  ## Creating a weekly interval column
  ####################################################################################################
  a.b.prod <- data.frame(abundance.base[1,])
  a.b.prod <- a.b.prod[-1,]
  
  
  for(j in 1:nrow(base.list)){
    
    abundance.base<-data.frame(subset(sealice.current, location == base.list[j,]))

    # Removing any dates with less than 30 fish
    
    
    ## Making julian dates
    abundance.base$date <- as.Date(with(abundance.base, paste(year, month, day, sep="-")), "%Y-%m-%d")
    abundance.base$date  <- julian(abundance.base$date) 
    datelist <-(abundance.base$date)
    ## Making a new column for weeklyinterval dates
    abundance.base$weeklyintvl<-rep(0, each = length(abundance.base$date))
    
    ## Finding the weekly intervals
    value <- abundance.base$weeklyintvl
    # all dates next to an empty column
    dat <- data.frame(datelist, value)
    # vector of all the unique dates
    dates = unique(dat$date)
    # vector for the number of rows for each date
    count <- c()
    
    for(i in 1:length(dates)){
      # length of the subset associated with each date
      n <- length(which(dat$datelist == dates[i]))
      # put the count into the empty vector
      count[i] <- n
    }
    # each unique date has a count of it's rows (assuming each row is a fish)
    output1 <- data.frame(dates, count)
    
    # Here you just turn dates into julian dates for ease later on
    #cbind to as.date version
    abundance.base$date <- as.Date(with(abundance.base, paste(year, month, day, sep="-")), "%Y-%m-%d")
    datelist <-(abundance.base$date)
    abundance.base$weeklyintvl<-rep(0, each = length(abundance.base$date))
    value <- abundance.base$weeklyintvl
    dat <- data.frame(datelist, value)
    dates = unique(dat$date)
    count <- c()
    for(i in 1:length(dates)){
      n <- length(which(dat$datelist == dates[i]))
      count[i] <- n
    }
    output2 <- data.frame(dates, count)
    
    #cbind outputs
    output.date <- cbind(output1,output2)
    output.date = subset(output.date, select = -c(count))
    
    #subset to remove dates with less than 30 fish
    remove.dates <- subset(output.date$dates.1, count < 30)
    #remove.dates <- as.Date(subset(output.date$dates, count <30)
    remove.dates <- data.frame(remove.dates)
    #remove dates from main data
    abundance.base$date  <- as.Date(abundance.base$date) 
    require(lubridate)
    class(remove.dates[,])
    class(abundance.base$date)
    list(remove.dates)
    
    #x# from the list above, input the dates into the filter function below by their column number
    if(nrow(remove.dates)>0){
      for(i in 1:nrow(remove.dates)){
        abundance.base <- abundance.base %>%
          filter(date != remove.dates[i,])#%>%
        #filter(date != as.Date(remove.dates[2,])) 
        #  filter(date != as.Date(remove.dates[,])) # unsure if this second line will cause problems
      }
    }
    
    #try <- abundance.base[(abundance.base$date != remove.dates[,]),]
    remove.dates
    unique(abundance.base$date)
    a.b.prod <- rbind(a.b.prod,abundance.base)
  }
  abundance.base <- a.b.prod # this is redundant but was kept to work with the rest of the code which calls on abundance.base


coho <- abundance.base

unique(chum$species)

abundance.base <- rbind(chum,chinook,coho)

colnames(abundance.base)
check <- abundance.base %>% group_by(date,location,species) %>% 
  summarize(Captures = sum(notNA(fish_id)))
view(check)
```
We bind the three species into a single dataframe in this line of code above.

## Finding the weekly interval
There are multiple years in the data. We need to subset for the appropriate year,
```{r Year Switch}
yr <- "2021"
#subset to adjust for year

abundance.base <- subset(abundance.base, year == yr)
```
The purpose of this code is to find the weekly intervals to provide the means of
the data within those dates. Labeling the weekly interval with the given row. 
Empty weekly interval column is being filled out by the function below. 
```{r Finding Weekly Interval}
# RM convert to julian
juliandates<-julian(abundance.base$date)

# RM find first day of sampling
firstday<-min(juliandates)

# RM The no. of weeks, rounded
no.weeks<-ceiling((max(juliandates)-min(juliandates))/7)

# RM A dataframe for the weekly interval data.
JDweeklyintervals<-rep(0, times = no.weeks)

# RM The weekly intervals are at multiples of 7 starting from the first day. 
for (i in 1:no.weeks) {
  if(i == 1){JDweeklyintervals[i]<-firstday+(6)} # This is to make sure that the first week only has 7 days, not 8.
  else{JDweeklyintervals[i]<-(firstday+(7*i)-1)} # This is to make sure that the following weeks are 7 days and the weekly interval date is the last day of the interval.
}

#Below converts julian to normal date. This is a useful bit of code to recycle... 
weeklyintervals<-as.Date(JDweeklyintervals, origin=as.Date("1970-01-01"))

#weekly intervals are given above to use for making weekly means. Now you can calculate means within those dates.

#may need to make the abundance.base into julian date
abundance.base$j.date<-julian(abundance.base$date)

JDweeklyintervalsloops<-c(0, JDweeklyintervals) #RM The 0 at the sart captures all the dates prior to the first weekly interval date (ie. the first 7 days of sampling)
abundance.base$weeklyintvl<-rep(0, each = length(abundance.base$date))
#using subsets to add data of appropriate date to the vectors

for (i in 1:(length(JDweeklyintervalsloops)-1)) {
  # RM Weekly interval subset
  loopintvl<-subset(abundance.base, abundance.base$j.date > JDweeklyintervalsloops[i] & abundance.base$j.date <= JDweeklyintervalsloops[i+1])
  # RM The index of the dates in this interval subset.
  positionsforaddingtoabundance.base<-which(abundance.base$j.date > JDweeklyintervalsloops[i] & abundance.base$j.date <= JDweeklyintervalsloops[i+1])
  # RM Assigning the latest date of a weekly interval to the weekly interval column of the main dataset 
  abundance.base$weeklyintvl[positionsforaddingtoabundance.base]<-JDweeklyintervalsloops[i+1]
  
  
}

#setting up counts
#x# make sure the coloumns selected below 12-26 correspond to actual
salmcounts<-subset(abundance.base[,c(11:25)])
#motile lice sub
motlice<-abundance.base[,c("Caligus_mot", "Caligus_gravid", "Lep_gravid", "Lep_nongravid", "Lep_male", "Lep_PAfemale", "Lep_PAmale", "unid_PA", "unid_adult")]
#cope lice sub
copes<-abundance.base[,c("Lep_cope", "Caligus_cope", "unid_cope")]
#chalimus lice sub
chals<-abundance.base[,c("chalA", "chalB", "chal_unid")]
#attached lice sub
attlice<-abundance.base[,c("Lep_cope","chalA","chalB","Caligus_cope","unid_cope","chal_unid")]
#total lice sub
abundance.base <- abundance.base %>% rowwise() %>%
  dplyr::mutate(Sum_all_lice = sum(c_across(Lep_cope:unid_adult)))


#Below gives columns of summed motiles, attached, copepodids, chalimus, and total counts. Useful for prevalence and abundance plots.
abundance.base$motsum<-rowSums(motlice, na.rm = TRUE)
abundance.base$copsum<-rowSums(copes, na.rm = TRUE)
abundance.base$chalsum<-rowSums(chals, na.rm = TRUE)
abundance.base$attachedsum<-rowSums(attlice, na.rm = TRUE)
abundance.base$sum_all_lice<-rowSums(salmcounts, na.rm = T)
abundance.base$motsum<- as.numeric(abundance.base$motsum)
abundance.base$copsum<- as.numeric(abundance.base$copsum)
abundance.base$attachedsum<-as.numeric(abundance.base$attachedsum)
abundance.base$sum_all_lice<-as.numeric(abundance.base$sum_all_lice)


#Below gives columns of summed motiles, attached, copepodids, chalimus, and total counts. Useful for prevalence and abundance plots.
abundance.base$motsum<-rowSums(motlice, na.rm = TRUE)
abundance.base$copsum<-rowSums(copes, na.rm = TRUE)
abundance.base$chalsum<-rowSums(chals, na.rm = TRUE)
abundance.base$attachedsum<-rowSums(attlice, na.rm = TRUE)
abundance.base$Sum_all_lice<-rowSums(salmcounts, na.rm = T)

#Last line in this chunk assembles the stages-tables to give the SUM of all lice stages by location

Motlicetab<-aggregate(motsum~location, data = abundance.base, sum)
Attlicetab<-aggregate(attachedsum~location, data = abundance.base, sum)
Coplicetab<-aggregate(copsum~location, data = abundance.base, sum)
Challicetab<-aggregate(chalsum~location, data = abundance.base, sum)
alltab<-aggregate(Sum_all_lice~location, data = abundance.base, sum)
# This is the final table for plots of sums! :)))
licetable<-data.frame(Motlicetab, Coplicetab[2], Challicetab[2], alltab[2], Attlicetab[2])

# This is a table for means by site and date

Motlicetab.mean.site.date<-aggregate(motsum~location + date, data = abundance.base, mean)
Attlicetab.mean.site.date<-aggregate(attachedsum~location + date, data = abundance.base, mean)
Coplicetab.mean.site.date<-aggregate(copsum~location+ date, data = abundance.base, mean)
Challicetab.mean.site.date<-aggregate(chalsum~location+ date, data = abundance.base, mean)
alltab.mean.site.date<-aggregate(Sum_all_lice~location+ date, data = abundance.base, mean)
# This is the final table for plots of means! :)))
licetable.mean.site.date<-data.frame(Motlicetab.mean.site.date, Coplicetab.mean.site.date[3], Challicetab.mean.site.date[3], alltab.mean.site.date[3], Attlicetab.mean.site.date[3])


#view to make sense

#make sure to check that sums make sense

#Last line in this chunk assembles the stages-tables to give the MEAN of all lice stages by location
mMotlicetab<-aggregate(motsum~location, data = abundance.base,mean)
mAttlicetab<-aggregate(attachedsum~location, data = abundance.base, mean)
mCoplicetab<-aggregate(copsum~location, data = abundance.base, mean)
mChallicetab<-aggregate(chalsum~location, data = abundance.base, mean)
malltab<-aggregate(Sum_all_lice~location, data = abundance.base, mean)
meanlicetable<-data.frame(mMotlicetab, mAttlicetab[2], mCoplicetab[2], mChallicetab[2], malltab[2])
meanlicetable<-meanlicetable[order(meanlicetable$location),]
secols<-data.frame(motsum = numeric(0), attsum = numeric(0), copesum = numeric(0), chalsum = numeric(0), allsum = numeric(0))
for (i in 1:length(meanlicetable$location)) {
  
  semeans.site.temp<-subset(abundance.base, location == meanlicetable$location[i])
  secols[i,1]<-sd(semeans.site.temp$motsum)/sqrt(length(semeans.site.temp$motsum))
  secols[i,2]<-sd(semeans.site.temp$attachedsum)/sqrt(length(semeans.site.temp$motsum))
  secols[i,3]<-sd(semeans.site.temp$copsum)/sqrt(length(semeans.site.temp$motsum))
  secols[i,4]<-sd(semeans.site.temp$chalsum)/sqrt(length(semeans.site.temp$motsum))
  secols[i,5]<-sd(semeans.site.temp$Sum_all_lice)/sqrt(length(semeans.site.temp$motsum))
}

names(secols)<-paste(c("SE.motile", "SE.attached", "SE.cops", "SE.chals", "SE.all"))
#line of code below shows error " Error in data.frame(..., check.names = FALSE) : 
#arguments imply differing number of rows: 5, 0
meanlicetablewithtotalse<-(cbind(meanlicetable, secols))
# This is the final table for plots of means! :)))
#liceofmeanlicetable<-data.frame(cbind(meanlicetable$motsum, meanlicetable$chalsum, meanlicetable$copsum))
allmeanlice <- data.frame(cbind(meanlicetable$motsum, meanlicetable$chalsum, meanlicetable$copsum, deparse.level = 1))
#names(allmeanlice[names(allmeanlice)== "X1"]) <- "motsum"
#names(allmeanlice[names(allmeanlice)== "X2"]) <- "chalsum"
#names(allmeanlice[names(allmeanlice)== "X3"]) <- "copsum"
#check order of names from grouped sites in best 2020, copy that orientation below
unique(abundance.base$location)
colnames(allmeanlice)<- c("mot.sum", "chalsum", "copsum")
rownames(allmeanlice) <- c( "Cypre River","North Meares","Bedwell Sound North","Ritchie Bay","Bedwell Sound Middle", "Bedwell Sound South","Moyeha","Cancer","White Pine")

#$% issue with Total showing up....
#making a shareable table of the lice means
getwd()

#save above table to csv with specified path = wd/data.output.path
#automated version

write.csv(meanlicetablewithtotalse,file.path(data.output.path,paste(i,"meanlicetable.bysite.csv")))

write.csv(licetable,file.path(data.output.path,paste(i,"totalsumslicetable.csv")))

```

