---
title: "Salmon Analyzed Markdown"
author: "Michael Lee"
date: "10/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Intro
This code creates the Makes mean prevalence, abundance, TS and forklength plots.
## Working Directory

The working directory sets up the paths for the file the code works out of. It
also creates the folders where we can access and create plots and the data files

```{r Working Directory}
wd <- "~/Sea-Lice-Analysis-2021"  
getwd()
setwd(wd)
folders <- c("Code", "Data", "OutputFigures", "OutputData")

# function to create folders below
for(i in 1:length(folders)){
  if(file.exists(folders[i]) == FALSE)
    dir.create(folders[i])
}

# we also need to store the paths to these new folders

code.output.path <- paste(wd, "/", folders[1], sep = "")
data.input.path <- paste(wd, "/", folders[2], sep = "")
figures.path <- paste(wd, "/", folders[3], sep = "")
data.output.path <- paste(wd, "/", folders[4], sep = "")

# our raw data is stored in different folders, lets make the paths
sealicedata.path <- paste(getwd(), "/Data", "/", sep = "")

# now we can access and save stuff to these folders!
```
## Code Cleaning

The code needs to clean up the data within the csv file. We also need to install
several packages to make the code work with the commands given. The cleaning of 
the code refers to the year, salmon species, location, and categories of sea 
lice.The purpose of this section is to make sure that all the unique categories 
are consistent. For example, there are locations where the names have an 
additional space in it, which R doesn't recognize as the same location. 

```{r Code Cleaning and Function}
#x# time to upload the datas into folder
sealicedata <- read.csv(paste(sealicedata.path, "/", "CCFS_SeaLice_Monitoring_2021.csv",
                              sep = ""), stringsAsFactors = FALSE)


#unhashtag to install packages below 
#install.packages(c("boot", "MASS","plyr","dplyr", "ggplot2", "tibble", "car", "reshape2",
#                  "epitools", "readxl", "tidyverse","arsenal")))
library(boot)
library(MASS)
library(plyr)
library(dplyr)
library(ggplot2)
library(tibble)
library(car)
library(reshape2)
library(epitools)
library(readxl)
library(tidyverse)
library(readr)
library(arsenal)
library(lubridate)
library(vtable)
library(nlme)
library(here)
library(ggthemes)


source("https://raw.githubusercontent.com/koundy/ggplot_theme_Publication/master/ggplot_theme_Publication-2.R")


warnings()

for(j in unique(sealicedata$species)){
  
  sealice <- subset(sealice, species == j)
#***************************CLEANING
#x#cleaning time
#adjusting datas***********************
sealicedata$year<-as.numeric(sealicedata$year)
#adjusting dates to date format
sealicedata$date <- as.Date(with(sealicedata, 
                                 paste(year, month, day, sep="-")), "%Y-%m-%d")
#height -> as.numeric
sealicedata$height<-as.numeric(sealicedata$height)
#making it all a df
sealicedata<-data.frame(sealicedata)
#changing na's to 0's
sealicedata[ , 12:26][is.na(sealicedata[ , 12:26] ) ] <- 0 
#col 1 to "fish_id"
names(sealicedata)[1]<-paste("fish_id")
#na's to 0 in sum_all_lice
sealicedata$sum_all_lice[is.na(sealicedata$sum_all_lice)]<-0

sealicedata <- sealicedata %>% rowwise() %>%
  dplyr::mutate(sum_all_lice = sum(c_across(Lep_cope:unid_adult)))

salmcounts <- sealicedata %>%
  select( Lep_cope, chalA, chalB, Lep_PAmale, Lep_PAfemale, Lep_male,
          Lep_nongravid, Lep_gravid, Caligus_cope, Caligus_mot, Caligus_gravid, unid_cope,
          chal_unid,unid_PA, unid_adult)

# RM defining categories of lice.

#motile lice sub
motlice<-sealicedata[,c("Caligus_mot", "Caligus_gravid", "Lep_gravid", "Lep_nongravid", "Lep_male", "Lep_PAfemale", "Lep_PAmale", "unid_PA", "unid_adult")]
#cope lice sub
copes<-sealicedata[,c("Lep_cope", "Caligus_cope", "unid_cope")]
#chalimus lice sub
chals<-sealicedata[,c("chalA", "chalB", "chal_unid")]
#attached lice sub
attlice<-sealicedata[,c("Lep_cope","chalA","chalB","Caligus_cope","unid_cope","chal_unid")]


#X# List character variables and go through one bye one
list(unique(colnames(sealicedata)))
#make sure year is consistent and case sensitive
list(unique(sealicedata$year))
#make sure names of species are correct
list(unique(sealicedata$species))
#fixing species names
sealicedata$species[sealicedata$species == "chum "]<- "chum"
sealicedata$species[sealicedata$species == "coho "]<- "coho"
sealicedata$species[sealicedata$species == "chinook "]<- "chinook"




#adjusting sample locations
#list locations
list(unique(sealicedata$location))

#adjusting names based on list output
#x#fix errors in names, do this by inputing the incorrect/ current name into the brackets, 
#and then the corrected version into the assigned end <-

#Bedwell Sound North Fix
sealicedata$location[sealicedata$location == "Bedwell Estuary "]<- "Bedwell Sound North"
sealicedata$location[sealicedata$location == "Bedwell estuary"]<- "Bedwell Sound North"
#Currently Bedwell Estuary is mapped as multiple locations, several close to the estuary and
#several near Bedwell Sound Middle: NEED TO FIX
#sealicedata$location[sealicedata$location == "Bedwell Estuary"]<- "Bedwell Sound North"
sealicedata$location[sealicedata$location ==  "Bedwell River"]<-"Bedwell Sound North"
sealicedata$location[sealicedata$location == "Bedwell Estuary 4"]<- "Bedwell Sound North"
sealicedata$location[sealicedata$location == "Bedwell estuary 4"]<- "Bedwell Sound North"

#Bedwell Sound Middle Fix
sealicedata$location[sealicedata$location == "Bedwell 2 "]<- "Bedwell Sound Middle"
sealicedata$location[sealicedata$location == "Bedwell estuary 3"]<- "Bedwell Sound Middle"
sealicedata$location[sealicedata$location == "Bedwell Estuary 3"]<- "Bedwell Sound Middle"
sealicedata$location[sealicedata$location == "Bedwell estuary 2"]<- "Bedwell Sound Middle"
sealicedata$location[sealicedata$location == "Bedwell Estuary 2"]<- "Bedwell Sound Middle"
sealicedata$location[sealicedata$location ==  "Bedwell 2"]<-"Bedwell Sound Middle"
sealicedata$location[sealicedata$location ==  "Sniffles"]<-"Bedwell Sound Middle"
sealicedata$location[sealicedata$location ==  "Sniffles 2"]<-"Bedwell Sound Middle"


#Bedwell Sound South Fix
sealicedata$location[sealicedata$location ==  "Bedwell 3"]<- "Bedwell Sound South"

#Cypre Fix
sealicedata$location[sealicedata$location == "Cypre "]<- "Cypre River"

#North Meares Fix
sealicedata$location[sealicedata$location == "Meares North"]<- "North Meares"

#White Pine Fix
sealicedata$location[sealicedata$location == "White Pine "]<- "White Pine"

#Ritchie Bay Fix
sealicedata$location[sealicedata$location == "Ritchie Bay "]<- "Ritchie Bay"

#Tranquil Fix
sealicedata$location[sealicedata$location == "Tranquil estuary"]<- "Tranquil Estuary"

list(unique(sealicedata$location))


#subset to adjust for year
#grouping data for a table of sums
sealice.current <- sealicedata
library(dplyr)
sumTable <- sealice.current %>% group_by(location,year) %>% count(fish_id)
bruh  <- data.frame(xtabs(n ~ year + location, sumTable))

#bruh <- tidyr::pivot_wider(sumTable, names_from = location, values_from = n)

colnames(bruh)
#ggplot(bruh, aes(x=factor(location),y=Freq, fill=year, label=Freq))+
geom_col(position=position_stack()) +labs(x="Location",y="Total Sum",fill = "Year",
                                          title="Juvenile Salmon Examined from 2018 - 2021")+
  theme_Publication()+  scale_fill_viridis_d(begin = 0.25, end = .95,direction = 1, option = "D")+     
  geom_text(size = 3, position = position_stack(vjust = 0.5))
####counts of fish analyzed by species
colnames(sealicedata)

#adjust for our focus species
sealice.current <- sealice.current<-data.frame(subset(sealice.current,
                                                      species == "coho"|species == "chum"|species == "chinook"|
                                                        species == "sockeye"|species == "pink"))


### END OF SET UP ###
### ## ABUNDANCE ESTIMATES ## #####

#Setting the cap for bootstrapping
n.boot.b<-1000

##ASSIGNING WEEKLY INTERVALS TO ALL THE dates in the abundance.base data set 
#weekly intervals.
#set up vectors to hold data

#X#beginning abundance plots, start bye creating a list function. 
#x#Start of Abundance Plot #1 for first Location in list
#Then determine how long the list is and replicate the following code that many times, only changing the x in base.list[x,] below
#you should replicate this whole code for every location sampled, unless there are not enough samples, rmeber each site needs a min of 30
base.list <- data.frame(unique(sealice.current$location))
list(base.list)
#starting with the first river in the list, 1
abundance.base<-subset(sealice.current, species == "chum" | species == "coho" | species == "chinook"| species == "sockeye" |species == "salmon")


# 1
####################################################################################################
## Taking out the dates where less than 30 fish were caught
## Creating a weekly interval column
####################################################################################################
a.b.prod <- data.frame(abundance.base[1,])
a.b.prod <- a.b.prod[-1,]


for(j in 1:nrow(base.list)){
  
  abundance.base<-data.frame(subset(sealice.current, location == base.list[j,]))
  # Removing any dates with less than 30 fish
  
  
  ## Making julian dates
  abundance.base$date <- as.Date(with(abundance.base, paste(year, month, day, sep="-")), "%Y-%m-%d")
  abundance.base$date  <- julian(abundance.base$date) 
  datelist <-(abundance.base$date)
  ## Making a new column for weeklyinterval dates
  abundance.base$weeklyintvl<-rep(0, each = length(abundance.base$date))
  
  ## Finding the weekly intervals
  value <- abundance.base$weeklyintvl
  # all dates next to an empty column
  dat <- data.frame(datelist, value)
  # vector of all the unique dates
  dates = unique(dat$date)
  # vector for the number of rows for each date
  count <- c()
  
  for(i in 1:length(dates)){
    # length of the subset associated with each date
    n <- length(which(dat$datelist == dates[i]))
    # put the count into the empty vector
    count[i] <- n
  }
  # each unique date has a count of it's rows (assuming each row is a fish)
  output1 <- data.frame(dates, count)
  
  # Here you just turn dates into julian dates for ease later on
  #cbind to as.date version
  abundance.base$date <- as.Date(with(abundance.base, paste(year, month, day, sep="-")), "%Y-%m-%d")
  datelist <-(abundance.base$date)
  abundance.base$weeklyintvl<-rep(0, each = length(abundance.base$date))
  value <- abundance.base$weeklyintvl
  dat <- data.frame(datelist, value)
  dates = unique(dat$date)
  count <- c()
  for(i in 1:length(dates)){
    n <- length(which(dat$datelist == dates[i]))
    count[i] <- n
  }
  output2 <- data.frame(dates, count)
  
  #cbind outputs
  output.date <- cbind(output1,output2)
  output.date = subset(output.date, select = -c(count))
  
  #subset to remove dates with less than 30 fish
  remove.dates <- subset(output.date$dates.1, count < 30)
  #remove.dates <- as.Date(subset(output.date$dates, count <30)
  remove.dates <- data.frame(remove.dates)
  #remove dates from main data
  abundance.base$date  <- as.Date(abundance.base$date) 
  require(lubridate)
  class(remove.dates[,])
  class(abundance.base$date)
  list(remove.dates)
  
  #x# from the list above, input the dates into the filter function below by their column number
  if(nrow(remove.dates)>0){
    for(i in 1:nrow(remove.dates)){
      abundance.base <- abundance.base %>%
        filter(date != remove.dates[i,])#%>%
      #filter(date != as.Date(remove.dates[2,])) 
      #  filter(date != as.Date(remove.dates[,])) # unsure if this second line will cause problems
    }
  }
  
  #try <- abundance.base[(abundance.base$date != remove.dates[,]),]
  remove.dates
  unique(abundance.base$date)
  a.b.prod <- rbind(a.b.prod,abundance.base)
}
abundance.base <- a.b.prod # this is redundant but was kept to work with the rest of the code which calls on abundance.base

abundance.base <- subset(abundance.base, location == "North Meares" | location == "Ritchie Bay" | location == "Cypre River")

speciestab <- abundance.base %>% group_by(year) %>% count(species)
speciestab  <- data.frame(speciestab)



# edited plot

ggplot(speciestab, aes(x=factor(year),y=n, fill=species))+
  geom_col(position=position_stack()) +labs(x="Year",y="Total Sum",fill = "Species",
                                            title="Juvenile Salmon Analyzed from 2018 - 2021")+
  theme_Publication()+  scale_fill_viridis_d(direction = 1, option = "D")


ggsave(filename=paste(j,capexamplot, "Captured&ExaminedLice_Yearly", ".png", sep = "_"))

}
```
The purpose of the function is to remove dates where >30 fish were caught. 
Turning dates into Julian to make it easier to process with R. Establishing 
weekly intervals to group dates and samples to take average from. 

This section of code also creates the plots for the mean abundance, prevalence,
and forklength.

