---
title: "Site Data Total Captured and Examined Markdown"
author: "Michael Lee"
date: "10/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro
The purpose of this code file is to provide the temperature and salinity plots
of the salmon analyzed in 2021, as these are factors in sea lice populations. 
The majority of the code is designed to clean the code and formatting to ensure 
it works optimally for R.  
## Working Directory

The working directory sets up the paths for the file the code works out of.

```{r Working Directory}
#set your wd here, MAKE SURE ITS SET TO YOUR PROJECT DATA BASE IN SESSION DROPDOWN MENU ABOVE
wd
getwd()
wd <- getwd()  # working directory
setwd(wd)
```

## Code Cleaning
The code needs to clean up the data within the csv file. We also need to install
several packages to make the code work with the commands given. The cleaning of 
the code refers to the year, salmon species, location, and categories of sea 
lice.The purpose of this section is to make sure that all the unique categories 
are consistent. For example, there are locations where the names have an 
additional space in it, which R doesn't recognize as the same location.
Makes a dataframe of the averages of temperature and salinity. Julian dates
aren't used in this code, since the data works without weekly intervals. 
There are 2 averages based on depth in water: (0m + 1m).

```{r Cleaning}
#TS PLOTS

#For TS plots, just change the spots that are marked (copy and paste )
sealicedata <- read.csv("Data/ClayoquotSeaLice_Site_Data.csv", header=TRUE, stringsAsFactors=FALSE)

#install.packages(c("boot", "MASS","plyr","dplyr", "ggplot2", "tibble", "car", "reshape2",
#                  "epitools", "readxl", "tidyverse","arsenal")))
library(boot)
library(MASS)
library(plyr)
library(dplyr)
library(ggplot2)
library(tibble)
library(car)
library(reshape2)
library(epitools)
library(readxl)
library(tidyverse)
library(readr)
library(arsenal)

#X#change year to current

#subset to adjust for year

sealicedata <- subset(sealicedata)



#adjusting names based on list output
#x#fix errors in names, do this by inputing the incorrect/ current name into the brackets,  
#and then the corrected version into the assigned end <-
unique(sealicedata$location)
sealicedata$location[sealicedata$location == "Cancer (Herbert)"]<- "Cancer"
sealicedata$location[sealicedata$location == "Bedwell Estuary "]<- "Bedwell Estuary"
sealicedata$location[sealicedata$location == "Meares North"]<- "North Meares"
sealicedata$location[sealicedata$location == "White Pine "]<- "White Pine"
sealicedata$location[sealicedata$location == "Ritchie Bay "]<- "Ritchie Bay"
sealicedata$location[sealicedata$locatizaon == "Cypre "]<- "Cypre River"
sealicedata$location[sealicedata$location == "Bedwell 2 "]<- "Bedwell 2"
sealicedata$location[sealicedata$location == "Bedwell Sound"]<- "Bedwell 3"
sealicedata$location[sealicedata$location == "Bedwell estuary"]<- "Bedwell Estuary"
sealicedata$location[sealicedata$location == "Tranquil estuary"]<- "Tranquil Estuary"
sealicedata$location[sealicedata$location == "Bedwell estuary 3"]<- "Bedwell 3"
sealicedata$location[sealicedata$location == "Bedwell estuary 4"]<- "Bedwell 4"
sealicedata$location[sealicedata$location == "Bedwell estuary 2"]<- "Bedwell 2"
sealicedata$location[sealicedata$location == "Bedwell Estuary"]<- "Bedwell Sound North"
sealicedata$location[sealicedata$location ==  "Bedwell 2"]<-"Bedwell Sound Middle"
sealicedata$location[sealicedata$location ==  "Bedwell 3"]<- "Bedwell Sound South"

unique(sealicedata$location)

tsaltemp <- sealicedata

tsaltemp$date <- as.Date(with(tsaltemp, paste(year, month, day, sep="-")), "%Y-%m-%d")


tsalsites<-unique(tsaltemp$location)
tsaltemp$salt_surf<-as.numeric(as.character(tsaltemp$salt_surf))
tsaltemp$salt_1m<-as.numeric(as.character(tsaltemp$salt_1m))
tsaltemp$temp_surf<-as.numeric(as.character(tsaltemp$temp_surf))
tsaltemp$temp_1m<-as.numeric(as.character(tsaltemp$temp_1m))
tsaltemp$date<-as.Date(tsaltemp$date, origin ="%Y-%m-%d")
year <- yr

```

## Function
The function subsets by the date, which will have multiple sites. This is 
important if you want to understand the oceanography of each site. This is 
because if you are averaging over all the individual sites, you get information 
about the region as a whole over time.
```{r Function}
for (d in 1:length(tsalsites)) {
  
  temptsal<-subset(tsaltemp, location == tsalsites[d])
  
  datetsal <- as.Date(unique(temptsal$date), origin ="%Y-%m-%d")
  tsd.site<- data.frame(meansurfsalt = numeric(0),
                        meansalt1 = numeric(0),
                        meantempsurf = numeric(0),
                        meantemp1 = numeric(0))
  
  
  #x# it looks like the objects being pulled from in this forloop are not returning any actual values, just NA's and 0's. I think it has to do with the plotsal df's, 
  #these issues seem to propogate into the plots below when tempdates is used
  # RM : I think the issue is that the length is based on the subset of data for one site, but is applied to all sites. I would recommend redoing this whole section as a forloop.
  for (j in 1:length(datetsal)) {
    #subsetting by the first date
    tempdates<-subset(temptsal, date == datetsal[j])  
    for (k in 1:4) {
      #taking the mean of the salinity/temp values for the one date
      tsd.site[j,k]<-mean(tempdates[,(6+k)])
    }
  }
  site.ts <- rep(tsalsites[d], each = length(tsd.site$meantemp1))
  tsd.site1 <- cbind(site.ts, tsd.site)
  if(d == 1) {tsdframe <- as.data.frame(tsd.site1)
  } else if(d > 1 ){tsdframe <- as.data.frame(rbind(tsdframe, tsd.site1))}
}

```
## Analysis
Examines and analyzes the grouped and summarized data by salmon species. Outputs
a temperature and salinity plot. 
```{r Analysis}
tsaltemp$salmon_captured[is.na(tsaltemp$salmon_captured)]<-0
tsaltemp$salmon_examined[is.na(tsaltemp$salmon_examined)]<-0
tsaltemp$salmon_captured <- as.numeric(tsaltemp$salmon_captured)
tsaltemp$salmon_examined <- as.numeric(tsaltemp$salmon_examined)
tsaltemp$salmon_captured <-  abs(tsaltemp$salmon_captured)
tsaltemp$salmon_examined <-  abs(tsaltemp$salmon_examined)



st(tsaltemp, vars = "salmon_examined")

is.na(tsaltemp$salmon_captured)

sum(tsaltemp$salmon_captured)
sum(tsaltemp$salmon_examined)

st(tsaltemp, group = "year",group.long = TRUE, vars = "salmon_captured", 
   summ = c('notNA(x)',
            'mean(x)',
            'median(x)',
            'propNA(x)', 'sum(x)'))
library(tidyverse)
library(ggrepel)
pacman::p_load(tidyverse,nlme,emmans,here)
pacman::p_load(ggthemes, ggplot2)

source("https://raw.githubusercontent.com/koundy/ggplot_theme_Publication/master/ggplot_theme_Publication-2.R")




# grouped and summarised data
tsaltemp1 <- tsaltemp %>% 
  group_by(year) %>% 
  summarise(salmon_captured = sum(salmon_captured), salmon_examined = sum(salmon_examined))
view(tsaltemp1)

tsaltemp2 <- tidyr::pivot_longer(tsaltemp1, cols=c('salmon_captured', 'salmon_examined'), names_to='variable', 
                           values_to="value")
print(tsaltemp2)

ggplot(tsaltemp2, aes(x=year, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge')

# edited plot

capexamplot<- ggplot(tsaltemp2, aes(x=factor(year),y=value, fill=variable))+
  geom_col(position=position_dodge()) +labs(x="Year",y="Total Sum",
                                            title="Juvenile Salmon Captured or Examined from 2018 - 2021" + 
  theme_Publication()+ scale_fill_viridis_d(option = "D",begin = 0.3, end = 0.9))

ggsave(filename=paste(capexamplot, "Captured&ExaminedLice_Yearly", ".png", sep = "_"))

#species by year and exam######
#cleaning
tsaltemp$salmon_captured[is.na(tsaltemp$salmon_captured)]<-0
tsaltemp$salmon_captured <- as.numeric(tsaltemp$salmon_captured)
tsaltemp$salmon_captured <-  abs(tsaltemp$salmon_captured)
#pink
tsaltemp$pink_examined[is.na(tsaltemp$pink_examined)]<-0
tsaltemp$pink_examined <- as.numeric(tsaltemp$pink_examined)
tsaltemp$pink_examined <-  abs(tsaltemp$pink_examined)
#coho
tsaltemp$coho_examined[is.na(tsaltemp$coho_examined)]<-0
tsaltemp$coho_examined <- as.numeric(tsaltemp$coho_examined)
tsaltemp$coho_examined <-  abs(tsaltemp$coho_examined)
#chinook
tsaltemp$chinook_examined[is.na(tsaltemp$chinook_examined)]<-0
tsaltemp$chinook_examined <- as.numeric(tsaltemp$chinook_examined)
tsaltemp$chinook_examined <-  abs(tsaltemp$chinook_examined)
#chum
tsaltemp$chum_examined[is.na(tsaltemp$chum_examined)]<-0
tsaltemp$chum_examined <- as.numeric(tsaltemp$chum_examined)
tsaltemp$chum_examined <-  abs(tsaltemp$chum_examined)
#sockeye
tsaltemp$sockeye_examined[is.na(tsaltemp$sockeye_examined)]<-0
tsaltemp$sockeye_examined <- as.numeric(tsaltemp$sockeye_examined)
tsaltemp$sockeye_examined <-  abs(tsaltemp$sockeye_examined)

#2021 check and breakdown
tsaltemp2021 <- subset(tsaltemp, tsaltemp$year == "2021")

colnames(tsaltemp2021)
tsaltemp2021 <- tsaltemp2021 %>% 
  group_by(year) %>% 
  summarise(salmon_examined = sum(salmon_examined), pink_examined = sum(pink_examined), 
            coho_examined = sum(coho_examined), chinook_examined = sum(chinook_examined), chum_examined = sum(chum_examined), sockeye_examined = sum(sockeye_examined))
view(tsaltemp2021)

library(vtable)

colnames(tsaltemp2021)
st(tsaltemp2021, group = "location",group.long = TRUE, vars = "salmon_captured", 
   summ = c('max(x)',
            'mean(x)',
            'median(x)',
            'propNA(x)', 'sum(x)'))

colnames(tsaltemp)
speciesset <- tsaltemp %>% 
  group_by(year) %>% 
  summarise(salmon_examined = sum(salmon_examined), pink_examined = sum(pink_examined), 
            coho_examined = sum(coho_examined), chinook_examined = sum(chinook_examined), chum_examined = sum(chum_examined), sockeye_examined = sum(sockeye_examined))
view(speciesset)

speciesset2 <- tidyr::pivot_longer(speciesset, cols=c('pink_examined','coho_examined', 'chinook_examined','chum_examined','sockeye_examined'), names_to='variable', 
                                 values_to="value")
print(speciesset2)

# edited plot

ggplot(speciesset2, aes(x=factor(year),y=value, fill=variable))+
  geom_col(position=position_stack()) +labs(x="Year",y="Total Sum",fill = "Species",
          title="Juvenile Salmon Examined from 2018 - 2021")+
            theme_Publication()+  scale_fill_viridis_d(direction = 1, option = "D")


ggsave(filename=paste(capexamplot, "Captured&ExaminedLice_Yearly", ".png", sep = "_"))
```

